%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.4 (Nov/17/2025)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% v1.4 author:
% Mae Brooks
%
% v1.4 repository:
% https://github.com/MaeBrooks/Resume
%
% IMPORTANT:
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ExplSyntaxOn
\NewDocumentCommand{\cvtag}{ m }{%
    \str_if_eq:noTF { #1 } { \tl_to_str:n {~{{~skill0~}}~} } {} {
        \tikz[baseline]\node[anchor=base, draw=blue!30, rounded~corners, inner~xsep=1ex, inner~ysep=0.75ex, text~height=1.5ex, text~depth=.25ex]{#1};
    }%
}
\ExplSyntaxOff

\newcommand{\sectiontitlespacer}{\vspace{2}}

\documentclass[]{resume-class}
\usepackage{fancyhdr}
\usepackage{changepage}
\usepackage{tikz}
\nonstopmode{}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

\namesection{Mae Brooks}{
  \href{mailto:home_in_the_rain+developer@proton.me}{home\_in\_the\_rain+developer@proton.me} | \href{tel:3868872770}{385-887-2770}

  \vspace{3}

  \begin{adjustwidth}{6em}{6em}
    \center{
      \footnotesize{Software Engineer with 6 years of experience building scalable web applications and internal tools from the ground-up, growing alongside coworkers, and exceeding expectations.}
    }
  \end{adjustwidth}
}

\vspace{8}

\begin{minipage}[t]{0.60\textwidth}

\section{Experience}
\sectiontitlespacer
\runsubsection{7 Factor LLC}
\descript{| Software Engineer II }
\location{May 2022 – Present | Atlanta, GA}
\vspace{\topsep}
\begin{tightemize}
\item{Leveraged Test Driven Development (TDD) to increase test coverage scores by 134\% across multiple clients.}
\item{Lead development efforts towards web accessiblity, resulting in a 79\% reduction in accessiblity errors.}
\item{Optimized build \& test scripts — \bold{Shaving 10,000+ minutes off of pipeline costs}, and reducing Largest contentful pain (LCP) by 2.3 seconds.}
\item{Increased fellow developer satisfaction as an elected as member of the developer experience team.}
\item{Reduced core application load time by 2 seconds by }
\item{Identified and resolved dependency issues, eliminating critical vulnerabilities}
\item{Partnered with other team leads to ship incremental releases, delivering web features on a bi-weekly cadence.}
\item{Collaborated with teams across multiple companies to conduct Agile, Kanban, and Scrum meetings.}     
\end{tightemize}
\sectionsep

\runsubsection{Service Robotics \& Technologies}
\descript{| Developer II}
\location{June 2020 – March 2022 | Nov Springfield, VA}
\begin{tightemize}
  \item{Engineered Phase II SBIR implementation to completion, resulting in an additional contract.}
  \item{Wrote deployment \& reporting scripts, \bold{reducing required onsite developer time from 5 days to 2}.}
  \item{Developed product for locating, controlling, and interfacing with devices in real time.}
  \item{Utlized Bitbucket Pipelines to host micro services in Azure.}
  \item{Generated documents and scripts for technical on—boarding.}
  \item{Protected privileged access to devices by leveraging Keycloak IAM.}
  \item{Completed stories alongside coworkers in an Agile environment.}
\end{tightemize}
\sectionsep

\runsubsection{Neddaxs}
\descript{| Lead Developer}
\location{August 2020 - October 2022}
\begin{tightemize}
  \item{Designed, developed, and hosted web apps.}
  \item{Raised 90k in revenue.}
  \item{Hired and tutored two part time developers.}
  \item{Met \& communicated with clients.}
\end{tightemize}
\sectionsep

\runsubsection{TxAnalytics}
\descript{| Developer I}
\location{July 2019 – June 2020 | Lehi, UT}
\begin{tightemize}
\item{Used Golang and React to allow users access to custom generated data reports.}
\item{Developed a database driver for a custom proprietary database utilizing TLS communication.}
\item{Increased customers sales by identifying key marketable attributes.}
\end{tightemize}
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

\section{Skills}
\sectiontitlespacer

\subsection{Programming}{
  \vspace{2}

  \cvtag{TypeScript/JavaScript}
  \cvtag{HTML/(S)CSS/}
  \cvtag{C}
  \cvtag{Go/Golang}
  \cvtag{Java}
  \cvtag{Rust}
  \cvtag{Lisp}
  \cvtag{PHP}
  \cvtag{SQL}
  \cvtag{NoSQL}
  \cvtag{RESTful API's}
  \cvtag{LaTeX}
}

\vspace{\topsep}
\subsection{Technology}
\vspace{2}
\cvtag{Angular}
\cvtag{ReactJS}
\cvtag{Vue}
\cvtag{Docker/Compose}
\cvtag{K8/Kubernetes}
\cvtag{PostgreSQL}
\cvtag{Cassandra}
\cvtag{MongoDB}
\cvtag{Bash/ZSH}
\cvtag{Gin}
\cvtag{WebGL \& Canvas}
\cvtag{GCP}
\cvtag{AWS}
\cvtag{D3JS}
\cvtag{NodeJS}
\cvtag{Typescript}
\cvtag{NPM}
\cvtag{Github Hooks}

\vspace{6}

\sectionsep

\section{Interests}
\sectiontitlespacer
\large{\textbf{Programming}} \\
\vspace{3}
Linux, Scripting, \& Learning
\vspace{2}

\large{\textbf{Volunteer Work}} \\
\vspace{3}
Food Pantry Volunteer
\vspace{2}

\large{\textbf{Reading}} \\
\vspace{3}
History, Sci—Fi, Documentation

\section{Projects}
\sectiontitlespacer
\runsubsection{Gren Lang}
\descript{| Tree-Sitter, Neovim, \& Emacs Maintainer}
\location{Jan 2023 – April 2026}
\vspace{\topsep}
\vspace{2}
\begin{tightemize}
  \item{Created and Maintained respective plugins for the Neovim \& Emacs text editors} 
  \item{Used Tree-Sitter to create a custom grammar}
  \item{Resolved bugs and issues brought up using Github issues}
\end{tightemize}

\section{Links}
\sectiontitlespacer
\vspace{4}
\begin{tightemize}
  \item{\href{https://github.com/MaeBrooks}{Github://MaeBrooks}}
  \item{\href{https://github.com/Maemacs}{Github://Maemacs}}
  \item{\href{https://www.linkedin.com/}{LinkedIn://MaeBrooks}}
\end{tightemize}

\end{minipage}
\end{document}
% \documentclass[]{article}
